\speculake: Hiding Malware in Speculative Execution

### 2018-05-07 paper/implementation.tex
Re-ran Bandwidth test and re-generated graph
add turing implementatino

\subsection{Turing Machine}

@@

We have implemented the AES decryption as a fundamental piece of the \speculake model,
and we demonstrate that the speed at which information can be decrypted using the speculative 
primitive is dependent on the configuration of the \speculake model. Specifical,
the channel width and the required minimum signal strength determine the maximum
throughput that can be acheived. As demonstrated in Figure~\ref{fig:spec_bandwidth} 
between 6 and 8 bits channel width provides an idea of the maximum speed at which the 
speculative primitive can be used with AES-NI instructions in the payload.

@@

\FigSpecBandwidth
% implementation 
%   Key Schedule expansion / obfuscation
%
% you can speculatively execute AES instructions

@@

% extract jump patterns
% sufficiency checks 
%
% trigger strength
%   - future work developing tools to determine sufficiency and strength
%
% OPENSSL TRIGGERING REVERSE SHELL SPASM PAYLOAD

>>>>

\subsection{Turing Machine}
\label{subsec:impl-turing}

We implemented a 5-state Busy Beaver Turing machine.
This implementation led to the discovery of many of the limitations and
capabilities of speculative execution.

We found that our implementation is able to examine the state and current symbol
on the Turing tape and make decisions based on these values as long as they are
in cache. The subtlety here is that in order to enter this speculative execution
the function pointer must be flushed from cache (causing the branch predictor to
incorrectly predict the target function as the destination). As such, care must
be taken to ensure that the function pointer and state to be used in the
speculative execution must be in separate cache lines.

In our model the real world keeps track of the Turing state and tape. The
speculative world uses this information to load a specific value into cache. The
real world then times the loading of these values to determine which value was
loaded speculatively. This value is then used to update the state and tape and
the process is repeated until a halt state is reached.

In order to have confidence the value loaded speculatively is correct we repeat
the execution a number of times and look for the value that has the quickest
real-world load time over each repetition, whichever value is quickest to load
the most is then determined to be the ``correct'' value.

Our Turing implementation discovered that only 50 repetitions is sufficient for
the real world to determine the correct value with over 80\% confidence.

We implemented the 5 state Busy Beaver configuration which requires over 47
million steps to complete. We were able to verify that the speculative world
could correctly compute 20 thousand steps with no errors.

@@

We have implemented the AES decryption as a fundamental piece of the \speculake model,
and we demonstrate that the speed at which information can be decrypted using the speculative 
primitive is dependent on the configuration of the \speculake model. Specifically,
the channel width and the required minimum signal strength determine the maximum
throughput that can be achieved. As demonstrated in Figure~\ref{fig:spec_bandwidth} 
between 6 and 8 bits channel width provides an idea of the maximum speed at which the 
speculative primitive can be used with AES-NI instructions in the payload.

@@

\FigSpecBandwidth

@@
